---
title: ""
toc: true
toc-location: right
toc-title: "On this page"
sidebar: mathematics
---

:::::: mathematics-hero

::: mathematics-intro
[HIGHER SECONDARY CERTIFICATE]{.mathematics-eyebrow}

# Higher Mathematics

Structured HSC Higher Mathematics lectures covering concepts, explanations, examples, exam questions and solutions.
:::

::::::

## Course Materials

:::::: mathematics-info-grid

::: mathematics-info-card
<i class="fa-solid fa-chalkboard-user"></i>

<h3>Lectures</h3>

<p>
Follow the lectures in sequence to build understanding topic by topic.
</p>
:::

::: mathematics-info-card
<i class="fa-solid fa-list-check"></i>

<h3>Exams</h3>

<p>
Apply the concepts through carefully selected questions and problems.
</p>
:::

::: mathematics-info-card
<i class="fa-solid fa-file-lines"></i>

<h3>Solutions</h3>

<p>
Review detailed solutions and understand the reasoning behind each step.
</p>
:::

::::::

## Lectures


```{r}
#| echo: false
#| warning: false
#| message: false

library(readr)
library(dplyr)
library(stringr)

sheet_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSS9xAr-Vm_XPEKsvPz9A1RWtIEW3R50nqcilODNggostrkW7ms5O84Dgrp9vheOer-K8Pu5PDtsgg2/pub?output=csv"

lectures <- read_csv(
  sheet_url,
  show_col_types = FALSE
)

lectures <- lectures %>%
  select(
    `CLASS NO.`,
    `LECTURE COMPLETE`,
    `CHAPTERS & PAPER`,
    CONTENT
  ) %>%
  filter(
    !is.na(`CLASS NO.`)
  )

```


:::::: mathematics-lecture-grid

```{r}
#| echo: false
#| results: asis

weekly_exam_no <- 0

for (i in seq_len(nrow(lectures))) {

  lecture_no <- lectures$`CLASS NO.`[i]
  lecture_complete <- lectures$`LECTURE COMPLETE`[i]
  chapter <- lectures$`CHAPTERS & PAPER`[i]
  content <- lectures$CONTENT[i]


  # ---------------------------------------------
  # Show only completed lectures
  # ---------------------------------------------

  if (
    is.na(lecture_complete) ||
    !str_to_lower(str_trim(as.character(lecture_complete))) %in%
      c("true", "yes", "1")
  ) {
    next
  }


  # ---------------------------------------------
  # Clean chapter
  # ---------------------------------------------

  if (is.na(chapter)) {
    chapter <- ""
  } else {
    chapter <- str_trim(as.character(chapter))
  }


  # ---------------------------------------------
  # Detect Weekly Exam
  # ---------------------------------------------

  is_weekly_exam <- FALSE

  if (!is.na(content)) {

    is_weekly_exam <- str_detect(
      str_to_lower(str_trim(as.character(content))),
      fixed(
        "weekly exam of previous lectures and problem solving",
        ignore_case = TRUE
      )
    )

  }


  # ---------------------------------------------
  # Weekly exam number
  # ---------------------------------------------

  if (is_weekly_exam) {

    weekly_exam_no <- weekly_exam_no + 1

    card_class <- "mathematics-lecture-card weekly-exam"

  } else {

    card_class <- "mathematics-lecture-card"

  }


  # ---------------------------------------------
  # Lecture number
  # ---------------------------------------------

  lecture_number <- as.integer(
    str_extract(
      as.character(lecture_no),
      "\\d+"
    )
  )


  # ---------------------------------------------
  # Lecture filename
  # ---------------------------------------------

  lecture_file <- sprintf(
    "lecture-%02d.html",
    lecture_number
  )


  # ---------------------------------------------
  # Start card
  # ---------------------------------------------

  cat(
    paste0(
      '<div class="',
      card_class,
      '">'
    ),
    "\n\n"
  )


  # ---------------------------------------------
  # Header
  # ---------------------------------------------

  cat(
    '<div class="lecture-header">',
    "\n\n"
  )


  # ---------------------------------------------
  # Header
  # ---------------------------------------------
  
  cat(
    '<div class="lecture-header">',
    "\n\n"
  )
  
  
  # ---------------------------------------------
  # Lecture / Weekly Exam number
  # ---------------------------------------------
  
  if (is_weekly_exam) {
  
    cat(
      paste0(
        '<span class="lecture-number">',
        sprintf(
          "WEEKLY EXAM %02d",
          weekly_exam_no
        ),
        '</span>'
      ),
      "\n\n"
    )
  
  } else {
  
    cat(
      paste0(
        '<span class="lecture-number">',
        sprintf(
          "LECTURE %02d",
          lecture_number
        ),
        '</span>'
      ),
      "\n\n"
    )
  
  }
  
  
  cat(
    '</div>',
    "\n\n"
  )



  cat(
    '</div>',
    "\n\n"
  )


  # ---------------------------------------------
  # Chapter / Paper
  # ---------------------------------------------

  if (chapter != "") {

    cat(
      paste0(
        '<div class="lecture-chapters">',
        chapter,
        '</div>'
      ),
      "\n\n"
    )

  }


  # ---------------------------------------------
  # Content
  # ---------------------------------------------

  if (
    !is.na(content) &&
    str_trim(as.character(content)) != ""
  ) {

    cat(
      paste0(
        '<div class="lecture-content">',
        str_trim(as.character(content)),
        '</div>'
      ),
      "\n\n"
    )

  }


  # ---------------------------------------------
  # Open button
  # ---------------------------------------------

  button_html <- paste0(
    '<a href="',
    lecture_file,
    '" class="mathematics-lecture-btn btn btn-primary">',
    'Open',
    '</a>'
  )


  cat(
    button_html,
    "\n\n"
  )


  # ---------------------------------------------
  # Close card
  # ---------------------------------------------

  cat(
    '</div>',
    "\n\n"
  )

}

```


::::::

<br>

::: contact-social

<a href="https://github.com/TurjoMahir"
   target="_blank"
   aria-label="GitHub">
   <i class="fa-brands fa-github"></i>
</a>

<a href="https://www.linkedin.com/in/md-foysal-uddin-3aa47a406/"
   target="_blank"
   aria-label="LinkedIn">
   <i class="fa-brands fa-linkedin-in"></i>
</a>

<a href="https://www.facebook.com/foysal.uddin.turjo.2005"
   target="_blank"
   aria-label="Facebook">
   <i class="fa-brands fa-facebook-f"></i>
</a>

<a href="mailto:foysaluddinturjo@gmail.com"
   aria-label="Email">
   <i class="fa-solid fa-envelope"></i>
</a>

:::